---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# EDAStat

<!-- badges: start -->
<!-- badges: end -->

The goal of the EDAStat package is to facilitate Exploratory Data Analysis (EDA) by providing functions to generate summary statistics and appropriate plots for a given dataset. It helps users understand their data by calculating outliers, identifying missing values, and creating visualizations.

## Installation

You can install the development version of EDAStat from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("nataliesz/summarystuff")
```

Make sure to install the required dependencies (dplyr, ggplot2, stats) before installing EDAStat.

## Usage

Given a variable and a dataset, `summary_stats()` function from the EDAStat package generates a statistical summary of the variable and provides that summary output in a list format.

```{r}
library(EDAStat)

summary_stats(mtcars$mpg, mtcars)
```

The EDAStat package function `distribution()` can generate a histograms of a specified variable and display the graphin the Plots section of RStudio

```{r}
distribution(mtcars$qsec, mtcars)
```

## License

`EDAStat` is licensed under the MIT License. See the [LICENSE](LICENSE) file for details.



