---
title: "Using the EDAStat package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the EDAStat package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Computing summary statistic of a variable in a dataframe

The main function of the EDAStat is to let the user generate a summary statistic of a variable(numeric or categorical).

```{r setup}
library(EDAStat)
```

The user then uses the summary_stats() function to generate summary statistics of a particular variable of interest by inputing the name of the dataset and the variable.

```{r}
summary_var <- summary_stats(mtcars$mpg, mtcars)
```

The objects returned by the summary_stats function is a list of summary statistics about the specified variable.

Additionally, the EDAStat package also creates appropriate plots and visualizations for user specified data. 

```{r}
distribution(mtcars$drat, mtcars)
```
This creates histogram for a numeric variable or a bar plot for the categorical varible from the user.
